Variance reduction for Markov chains via martingale representations

### 2020-05-04 aap/Revision/vr-mcmc-revision-new-new.tex
update

$$
\rho = \exp\left\{\frac{\gamma m}{4}\frac{\log{(1-\varepsilon)}}{\log{(1-\varepsilon)} + \log{(\exp{\left(-\frac{m\gamma}{2}\right)} + \frac{2b}{K^2+2})}}\right\}
$$
where $K_2 > 0$ is from Lemma~\ref{lem:quadratic_behaviour} and $K>0$ is a positive parameter such that 
$$
K^2 > 4\frac{2K_2^2(L+m) + d + m}{m}
$$
\end{lem}

>>>>

$$
\rho = \exp\left\{-\frac{\gamma m}{4}\frac{\log{(1-\varepsilon)}}{\log{(1-\varepsilon)} + \log{(\exp{\left(-\frac{m\gamma}{2}\right)} + \frac{2b}{K^2+2})}}\right\}
$$
where $K_2 > 0$ is from Lemma~\ref{lem:quadratic_behaviour} and $K>0$ is a positive parameter such that 
$$
K^2 > 4\frac{2K_2^2(L+m) + d + m}{m}
$$
\end{lem}
